\newpage
\section{Abstract syntax and static semantics}
\genHeader
\label{sec: staticSemantics}

The first step in creating any metamodel is defining the abstract syntax, also known as the type graph. This involves defining each class, its attributes,
references, and method signatures.

If you completed the demo in Part I, your Eclipse workspace will look slightly different than ours depicted in the screenshots. In an effort to keep things as
clear as possible, we have removed those files from our package explorer, but still recommend keeping them for future reference. 

Additionally, if you're continuing from the visual syntax, you can begin modeling this project in two different ways. You can either develop your metamodel in
the same workspace as the demo, or create a new metamodel. If you choose to do this, please note that the steps are exactly the same, but our package explorers
may not exactly match. This handbook has assumed you prefer the latter.

\fancyfoot[RO]{ $\triangleright$ \hyperlink{static:starting vis}{Next [visual]\hspace{0.2cm}} \\ $\triangleright$ \hyperlink{static:starting tex}{Next
[textual]}}

\input{../2_staticSemantics/1_newStart/gettingStarted_vis}
\input{../2_staticSemantics/1_newStart/gettingStarted_tex}

\input{../2_staticSemantics/2_definingClasses/defClasses_vis}
\input{../2_staticSemantics/2_definingClasses/defClasses_tex}

\input{../2_staticSemantics/3_connectingClasses/references_splash}

\input{../2_staticSemantics/4_creatingMethods/methods_vis}
\input{../2_staticSemantics/4_creatingMethods/methods_tex}

\input{../2_staticSemantics/5_validation/vis_EAValidation/validateVis}
\input{../2_staticSemantics/5_validation/tex_eclipseValidation/validateTex}

\input{../2_staticSemantics/staticReview} 
