\genHeader
\section{Conclusion and next steps}

\vspace{0.5cm}

Congratulations -- you've reached the end of eMoflon's introduction to unidirectional model transformations! You've learnt that SDMs are declared as
\emph{activities}, which consist of \emph{activity nodes}, which are either \emph{story pattern}s or \emph{statement nodes} (for method calls).
\emph{Patterns} are made up of \emph{object} and \emph{link variables} with appropriate attribute constraints. Each of these variables can be given
different \emph{binding states}, binding operators, and can be marked as negative (for expressing NACs).

\vspace{0.5cm}

To further test your amazing story driven modelling skills, challenge yourself by:
\begin{itemize}
\item Adjusting \texttt{check} to eject the card from the box if it is guessed correctly and contained in the last partition (to signal it's been learnt). Do
you know how \texttt{check} currently handles this?
\item Editing \texttt{Partition.empty()} to include a method call to \texttt{removeCard}, thus reusing this previous SDM
\item Modifying the GUI source files to execute all methods
\end{itemize}

\vspace{0.5cm}
	
If you have any comments, suggestions, or concerns for this part, feel free to drop us a line at \href{mailto:contact@moflon.org}{contact@moflon.org}.
Otherwise, if you enjoyed this section, continue to Part IV to learn about Triple Graph Grammars, or Part V for Model-to-Text Transformations.
The final part of this handbook -- \Cref{chap:misc} -- contains a full glossary, and tips and tricks in EA which you might find useful when creating SDMs in the future.

Cheers!
