\newpage
\subsection{Connecting your classes}
\genHeader
\hypertarget{static:references splash}{}

At this point, you've declared your types and their attributes, but what good are those if you can't connect them to each other? We need to create some
\emph{EReferences}\define{EReference}!

There are four properties that must be set in order to create an EReference: the target and source \emph{Role}, \emph{Navigability}, \emph{Multiplicity} and \emph{Aggregation}, all of which are declared differently in each syntax, but let's first review the concepts since they're basically the same.

A \emph{Role}\define{Role} clarifies which way a reference is `pointing.' In other words, the \emph{source} and \emph{target} roles determine the direction of the
connection.

\emph{Navigable}\define{Navigability} ends are mapped to class attributes with getters and setters in Java, and therefore \emph{must} have a specified name and
multiplicity for successful code generation. Corresponding values for \emph{Non-Navigable} ends can  be regarded as additional documentation, and do not have
to be specified.

The \emph{Multiplicity}\define{Multiplicity} of a reference controls if the relation is mapped to a (Java) collection (`\texttt{*}',~`\texttt{1..*}',~`\texttt{0..*}'), or to a single
valued class attribute (\texttt{`1'}, \texttt{`0..1'}). We'll explain this setting in detail later.

The \emph{Aggregration}\define{Aggregation} values of a reference can be either none or com\-po\-site. Composite means that the current role is that of a
\emph{container}\define{Container} for the opposite role. You'll see in our example that \texttt{Box} is a container for several \texttt{Partition}s.
This has a series of consequences: (1) every element must have a container, (2) an element cannot be in more than one container at the same time, and (3) a
container's contents are deleted together with the container. Conversely, non-composite (denoted by ``none") means that the current role is not that of a container,
and the rules for containment do not hold (in other words, the reference is a simple `pointer').


\jumpDual{static:references vis}{static:references tex}

\input{../2_staticSemantics/3_connectingClasses/references_vis}

\input{../2_staticSemantics/3_connectingClasses/references_tex}
