\chapter{Modelling a Memory Box}
\label{chap:membox}

What is a memory box?  Figure, why is the example interesting to showcase
metamodelling and model transformations?

What is a model? Metamodel? Instances? Metalevels? Abstractionlevels? Figure
from master thesis.  Always with respect to our concrete example.

Comparison of normal (direct) software development to model-driven software
development, advantages, motivation, product lines, etc

What exactly is model-driven software development?

References to papers, books

\section{A Language Definition Problem?}

What is concrete syntax?  Abstract syntax?  Static semantics?  Dynamic
semantics?  Viewing metamodels as languages, metametamodels as metalanguages,
models as valid words of a certain language.

\section{Static Semantics with Ecore}

Class diagram for memory box, eclass, ereference, Ecore as metametamodel,
epackages, composites, eopposite.

\section{Dynamic Semantics with SDM}

Graph transformations?  Declarative rules?  Graph grammar?  SDMs?

Based on concrete SDM for memory box:

\subsection*{Activities, Activity Nodes and Edges}

\subsection*{Object and Link Variables}

\subsection*{Expressions}

\subsection*{Statement Nodes}

\subsection*{Start and Stop Nodes}

\subsection*{Attribute Constraints}

\subsection*{Negative Application Conditions}

\subsection*{ForEach Activity Nodes}

\subsection*{Binding Expressions}

\section{Completing the System with a GUI}

Interaction with libraries, frameworks and hand-crafted code.