\newpage
\hypertarget{TGGSchema}{}
\section{Specifying a TGG schema}
\genHeader

Great! Now we can get started. The first step to a completing any TGG is to model the correspondence component of your triples.\define{Link \\ Metamodel}This
correspondence, or \emph{link metamodel}, is made up of \emph{correspondence types}\define{Correspondence Types}which connect classes between the source and
target metamodels. These special types can also be thought of as traceability links.

While the link metamodel is really just a standard metamodel, we use a slightly different concrete syntax and naming convention to represent it.\define{TGG
Schema}The overall metamodel triple consisting of the relevant parts of the source, correspondence, and target metamodels is called the \emph{TGG schema}.

A TGG schema can be viewed as the (metamodel) triple to which all new triples must conform. In less technical lingo, it gives an abstract view on the
relationships (\emph{correspondence}) between two metamodels or domains. A doman expert should be able to understand why certain connected elements are related,
irrespective of how the relationship is actually established by TGG rules, just by looking at the TGG schema. Please note that all other information in the
source and target metamodels, such as attributes, methods, and references, are shown by default in the TGG schema.

In our example, our source graph is \texttt{LearningBoxLanguage}, and our target is \texttt{DictionaryLanguage}. Given that we have both of these things, in
this section, we will finally build our link metamodel by completing the relationships between the two.

\jumpDual{schema vis}{schema tex}

\input{../2_schema/visSchema.tex}

\input{../2_schema/texSchema.tex}
