\newpage
\section{Abstract syntax and static semantics}
\genHeader
\label{sec: staticSemantics}

The first step in creating any metamodel is defining the abstract syntax, also known as the type graph. This involves defining each class, its attributes,
references, and method signatures.

If you completed the demo in Part I, your Eclipse workspace will look slightly different than ours depicted in the screenshots.
In an effort to keep things as clear as possible, we have removed those files from our package explorer, but still recommend keeping them for future reference. 

Additionally, if you're continuing from the demo, you can begin modelling this project in two different ways. 
You can either develop your metamodel in the same workspace as the demo, or create a new one.
Either way, please note that the steps are exactly the same, but our project browsers in EA may not exactly match.
This handbook has assumed you prefer the latter.


\input{../../org.moflon.doc.handbook.02_leitnersLearningBox/2_staticSemantics/1_newStart/gettingStarted_vis}

\input{../../org.moflon.doc.handbook.02_leitnersLearningBox/2_staticSemantics/2_definingClasses/defClasses_vis}

\input{../../org.moflon.doc.handbook.02_leitnersLearningBox/2_staticSemantics/3_connectingClasses/references_splash}

\input{../../org.moflon.doc.handbook.02_leitnersLearningBox/2_staticSemantics/4_creatingMethods/methods_vis}

\input{../../org.moflon.doc.handbook.02_leitnersLearningBox/2_staticSemantics/5_validation/vis_EAValidation/validateVis}

\input{../../org.moflon.doc.handbook.02_leitnersLearningBox/2_staticSemantics/staticReview} 
