\newpage
\section{Specifying a TGG schema}
\genHeader

The first step on the way to a TGG is to model the correspondence component of your triples. The correspondence or link metamodel consists of
\emph{correspondence types} which connect classes from the source and target metamodels. In our case, our source metamodel is \texttt{LearningBoxLanguage} and
target \texttt{DictionaryLanguage}. Remember that a \emph{correspondence type} can be considered as a traceability link which relates the elements from the
source and target components. Although the correspondence metamodel is actually just a normal metamodel, we use a slightly different concrete syntax to present
it and adhere to certain naming conventions.\define{TGG Schema}The metamodel triple consisting of (relevant parts of) the source metamodel, the correspondence
metamodel and (relevant parts of) the target metamodel is called a \emph{TGG schema}.

\begin{enumerate}
  
\item[$\blacktriangleright$] If you've worked through the tutorial until now, you can import \texttt{Dic\-tion\-ary\-Language} into the EAP file containing
\texttt{Learning\-Box\-Language} or vice-versa. Important is that \emph{both} metamodels are in the \emph{same} EAP file so we can specify an integration with
TGGs. How to transfer projects between EAP files is explained in {\bf blah}

\item[$\blacktriangleright$] If you're just joining us for TGGs, or just don't want to go through the trouble of transferring the EA projects, simply import the
prepared metamodel project ``For\-Chapter\-On\-TGG/Learning\-Box\-2\-Dic\-tion\-ary" (in the \texttt{eMoflon\-Tutorial.zip} you downloaded with this tutorial)
into your Eclipse workspace .

\end{enumerate}

\input{../1_schema/visSchema.tex}

\input{../1_schema/texSchema.tex}

\newpage

\subsection{Shema concluded}
\genHeader

A TGG schema can be viewed as the metamodel triple to which all created triples must conform. In less technical lingo, it gives an abstract view on the
relationship or \emph{correspondence} between two metamodels or domains. Just by looking at the TGG schema, a domain expert should understand \emph{why} the
connected elements are related, irrespective of \emph{how} the relationship is actually established by TGG rules (coming up next). Note that all other
information in the source and target metamodels such as attributes, methods and references between classes are also visualized per default in the TGG schema --
just in case you were wondering where all the attributes and references suddenly came from.
