\newpage
\hypertarget{TGGSchema}{}
\section{Creating your TGG schema}
\genHeader

Now that the necessary source and target metamodels are in the same workspace, there are several different ways to begin specifying a TGG. We're going to begin
with modeling the correspondence component of the triple language. This correspondence, or \emph{link metamodel},\define{Link \\ Metamodel} specifies
\emph{correspondence types},\define{Correspondence Types} which will be used to connect specific elements of the source and target metamodels. These
correspondence elements can also be thought of as \emph{traceability links}.

While the link metamodel is technically a standard metamodel, eMoflon uses a slightly different naming convention and concrete syntax to represent it. The
overall\define{TGG Schema} metamodel triple consisting of the relevant parts of the source, link, and target metamodels is called a \emph{TGG schema}.

A TGG schema can be viewed as the (metamodel) triple to which all \emph{new} triples must conform. In less technical lingo, it gives an abstract view on the
relationships (correspondence) between two metamodels or domains. A domain expert should be able to understand why certain connected elements are related,
irrespective of how the relationship is actually established by TGG rules, just by looking at the TGG schema. 

In our example schema, we will create a link between our source \texttt{Box} and target \texttt{Dictionary} to express that these two container elements are
related.

\jumpDual{schema vis}{schema tex}

\input{../3_schema/visSchema.tex}

\input{../3_schema/texSchema.tex}
