\newpage
\section{Expanding LeitnersLearningBox}
\genHeader

\emph{Introduce the problem: four partitions. Integrator doesn't help, what do? Protocol! Explain what went wront, new rule! Run again, show protocol round
two, and look! it runs fine.}

At this point, we now have a working TGG transformation for Dictionary into box with three partitions, and a box with \emph{precisely} three partitions into a
Dictionary. The only forseeable problem here is that\ldots well\ldots exactly three partitions is slightly unrealistic for a proper study box. After all, the
more you need to practice a subject, the more partitions you should have so you are quizzed again and again.

Problem: exactly three partition is kind of unrealistic for a box. After all, the more you want to practice a word, or a set of words, the more partitions you
should have so that you are asked again and again what the answer is. But no matter - our current rule needs at least three to work, right? If a new one is
added, it should still work for those three. Lets confirm by adding a fourth partition to \texttt{source.xmi}. Give it an index of three, set its prev value to
partition2, and set the next value in partition2 to partition3. also set its back to QuestionThree and face to answer dreisave and run TGGMain. it failed (say,
what?!). Even though it was able to find a solution to the first threee, there was no way it could have connected number 4 successfully, resulting in a dangling
edge, which fujaba does not allow.

But why didn't at least the first set of card from partitions 0, 1, 2. Work? Dangling edges - predicts that there will be no way to repair it, so it ends te
whole operation.

While we addressed in index issue in our implemenation code (anzthing above 2 would be assigned as index 2), that only took care of one direction (card to
entry) in the other direction, it simly has no idea what needs to be created /made. 

Lets consider extending the rule so it could handle a fourth card. It would be as simple as including another partition in our rule and connecting it proberly.
But what if we wanted a fith? a sixth?  This obviously won't work -- there will always be an n+1 partition that needs to be resolved.

Instead, let's create a new rule. After all, the protocol is bound to try EVERY possilbilty before continuing. that means, if the first rule fails, it will try
to apply this one, and it will succeed.

\jumpDual{allCards vis}{allCards tex}

\input{../6_protocol/visNewRule}

\input{../6_protocol/texNewRule}

\input{../6_protocol/protocolClose}
