\newpage
\hypertarget{sec:conBran}{}
\section{Conditional branching}
\genHeader

When working with SDMs, you'll often find yourself needing to decide which statement(s) to execute based on the return value of an arbitrary (black box)
operation, as we saw in \texttt{check}. In our example so far, we have implemented these constructs via SDM \emph{pattern matching}. 

With eMoflon however, there is an alternate way to construct these black boxes. In fact, this feature is yet another way of integrating handwritten java code
with your SDM. We can invoke methods directly from an \emph{if} statement. The only ``rule'' of this feature is that the method must return an
\texttt{EBoolean} to indicate \texttt{Success} or \texttt{Failure}, corresponding to \texttt{true} or \texttt{false}, respectively. Any other types imply
\texttt{Failure} if the return value of the method is \texttt{null}. It follows that void methods cannot be used for branching -- an exception will be thrown
during code generation (if you ignored the validation error).

Unfortunately, you can't simply invoke a method from a standard activity node. Instead, you must use a new type of activity node, a \emph{statement
node}.\define{Statement Node}Statement nodes can be used to invoke methods and provide a means of invoking libraries and
arbitrary Java code from SDMs. Please note that we do not differentiate at this point between methods that are implemented by hand or via an SDM. Thus,
statement nodes can of course be used to invoke other SDMs via a \emph{MethodCallExpression}. Most importantly, statement nodes enable \emph{recursion}, as the
current SDM can be invoked on \texttt{this} with appropriate new arguments. In essence, this type of node is only used to guarantee a specific action
between \emph{activity nodes}, and does not extend the current set of matched variables. They can however, be used as a conditional by branching on
whatever value the method returns.

Let's reconsider \texttt{grow}, the method we just completed that adds a new partition to our box. Reviewing either Fig.~\ref{fig:growComplete} (Visual) or
Fig.~\ref{fig:patternComplete} (Textual), the current pattern assumes there are already at least two partitions in \texttt{box} (the
\texttt{firstPartitionInBox} and \texttt{LastPartitionInBox}). What would happen if \texttt{box} had only one, or even no partitions at all? The pattern would
\emph{never} find a match!

To fix this problem, let's modify \texttt{grow} so that if the original match fails, we initialize two new partitions (the first and last), but \emph{only} if
it failed due to the box being completely empty. In other words, if \texttt{box} has e.g., only one partition (an invalid state that cannot be reached by
growing from zero partitions), it is considered invalid and no longer be grown.

\jumpDual{conBran vis}{conBran tex}

\input{../09_conditionalBranching/visConBran}

\input{../09_conditionalBranching/texConBran}

\input{../09_conditionalBranching/initializeBoxNotes}
