\newpage
\hypertarget{sec:conBran}{}
\section{Conditional branching}
\genHeader

When working with SDMs, you'll often find yourself needing to decide which statement(s) to execute based on the return value of an arbitrary (black box)
operation, as we saw in \texttt{check}. In our example so far, we have implemented these constructs via SDM \emph{pattern matching}. 

With eMoflon however, there is an alternate way to construct these black boxes. In fact, this feature is yet another way of integrating handwritten java code
with your SDM! The only ``rule'' of this feature is that your method must return an \texttt{EBoolean}: \texttt{Success} or \texttt{Failure}, 
corresponding to \texttt{true} or \texttt{false}, respectively. Any other values will set \texttt{Failure} to \texttt{null}. It follows that void methods cannot
be used for branching - an exception will be thrown during execution. \emph{Statement nodes} are used as the \emph{if} construct's conditional by branching on
whatever value the invoked method returns.

Let's reconsider \texttt{grow}, the method we just completed that adds a new partition to our box. Reviewing Fig.~\ref{fig:growComplete}, the current pattern
assumes there are already at least two partitions in \texttt{box}. What would happen if it had only one, or even no partitions at all? The pattern would \emph{never}
find a match. To correct this problem, lets modify \texttt{grow} so that if the original match fails, we initalize two new partitions (a first and last), but
\emph{only} if it failed due to the box being completely empty. In other words, if \texttt{box} has only one partition (we view this as an invalid state that
cannot be reached by growing), it cannot be grown.

\jumpDual{conBran vis}{conBran tex}

\input{../09_conditionalBranching/visConBran}

\input{../09_conditionalBranching/texConBran}
