\newpage
\subsection{Connecting your classes}
\genHeader
\hypertarget{static:references splash}{}

\texttt{}
\emph{}

At this point, you've declared your necessary classes and attributes, but what good are those if they can't communicate with one another? We need to create some
\emph{EReferences}!

There are 4 settings that must be set in order to create an EReference: \emph{Navigation}, \emph{Aggregation}, \emph{Multiplicity}, and \emph{Role}. As you can probably guess,
they're declared differently in each syntax, but let's review the concepts since they're the same.

Firstly, \texttt{Navigable} ends are mapped to class attributes with getters and setters in Java, and therefore \emph{must} have a specified name and
multiplicity for successful code generation. Corresponding values for \texttt{Non-Navigable} ends can  be regarded as additional documentation and do not have
to be specified.

Second, the \texttt{Multiplicity} refers to that of a reference\footnote{Don't get multiplicity of a reference confused with the multiplicity of an element!
Multiplicity of an element defines the permitted range of individual instances, rather than of a class relation.}. It controls if the relation is mapped to a Java Collection
(\texttt{*},~\texttt{1..*},~\texttt{0..*}), or to a single valued class attribute (\texttt{1}, \texttt{0..1}). We'll explain this setting in detail when you
encounter them in your syntax instructions.

Lastly, in Ecore, the \texttt{Aggregration} values of a reference can be \texttt{none}, \texttt{shared}, or \texttt{com\-po\-site}. Composite means that the
current role is that of a \emph{container} for the opposite role. You'll see in our example that \texttt{Box} is a container for \texttt{Partition}s. This has a series of
consequences: (1) every element must have a container, (2) an element cannot be in more than one container at the same time, and (3) a container's contents are
deleted together with the container. Conversely, non-composite (\texttt{none}) means that the current role is not that of a container, and the rules for
containment do not hold (in other words, the reference is set a simple `pointer'). The \texttt{shared} setting is beyond the scope of this handbook.

\fancyfoot[RO]{ $\triangleright$ \hyperlink{static:references vis}{Next [visual]\hspace{0.2cm}} \\ $\triangleright$ \hyperlink{static:references tex}{Next [textual]}}
\input{../2_staticSemantics/3_connectingClasses/references_vis}
\input{../2_staticSemantics/3_connectingClasses/references_tex}