\newpage
\section{Specifying a TGG schema}
\genHeader

As you might assume, the first step to a completing a TGG is to model the correspondence component of your triples. The correspondence, or \emph{link metamodel}
consists, of \emph{correspondence types} which connect classes between the source and target metamodels. In our case, our source metamodel is our
current running example, \texttt{LearningBoxLanguage}, and our target is \texttt{DictionaryLanguage}, which we'll have you import into your project in the next
few steps. Remember, a \emph{correspondence type} can be considered as a traceability link. While the correspondence metamodel is really just a standard
metamodel, we use a slightly different concrete syntax to present it, and adhere to certain naming conventions.\define{TGG Schema}The overall metamodel triple
consisting of the relevant parts of the source, correspondence, and target metamodels is called the \emph{TGG schema}.

A TGG schema can be viewed as the metamodel triple to which all created triples must conform. In less technical lingo, it gives an abstract view on the
relationship or \emph{correspondence} between two metamodels or domains. Just by looking at the TGG schema, a domain expert should understand \emph{why} the
connected elements are related, irrespective of \emph{how} the relationship is actually established by TGG rules (coming up next). Note that all other
information in the source and target metamodels such as attributes, methods and references between classes are also visualized per default in the TGG schema --
just in case you were wondering where all the attributes and references suddenly came from.


\input{../2_schema/visSchema.tex}

\input{../2_schema/texSchema.tex}
