\newpage
\phantomsection
\addcontentsline{toc}{section}{Glossary}
\hypertarget{glossary}{}

\vspace{1cm}
{\Huge \bf Glossary}
\vspace{1cm}

\begin{description}

\item[\bf Activity]
Container element that describes the behavior and structure for one method.

\item[\bf Activity Edge]
A directed connection between elements (such as activity and stop nodes) within an \emph{activity} as a part of control flow.

\item[\bf Activity Node]
Describe and contain actions that manipulate the states of objects.

\item[\bf Assignments]
Used in context to set attributes and variables.

\item[\bf Attribute Constraint]
A non-structural contraint that must be satisfied for a story pattern to match. Specified by an \texttt{:=} operator.

\item[\bf Binding State]
Can be either \emph{bound} or \emph{unbound/free}. See \emph{Bound vs Unbound}.

\item[\bf Binding operator]
Determines purpose of pattern variable, whether they will be just \emph{checked}, \emph{created}, or \emph{destroyed} during pattern matching.

\item[\bf Binding Semantics]
Determine if an object variable \emph{must} exist (\emph{madatory}), may not exist (\emph{negative}; see \emph{NAC}), or either or (\emph{optional}) during
\emph{pattern matching}.

\item[\bf Bound vs Unbound]
Bound variables are completley determined by the current context, whereas unbound (free) variable matches have to be determined by the \emph{pattern matcher}.
\texttt{This} and parameter values are always bound.

\item[\bf Dangling Edges]
An edge stemming from the source role of a reference with no target, or vice versa. Existence immediately make graphs invalid.

\item[\bf EA]
Enterprise Architect; The UML visual modeling program used with our tool.

\item[\bf Edge Guards]
Construct of conditional branching, these block actions in node at end of edge until a specific condition is satisifed.

\item[\bf Link Variable]
Placeholders for object references during pattern matching. Syntax: [aggregration type][reference name]:[target object]

\item[\bf Literal Expression]
Can express any arbitrary text, though an effort should be made to use only for constants (literals).

\item[\bf MethodCallExpression]
Helper method that calls any method defined in a different class than current method in an \emph{EA} Project.

\item[\bf NAC]
Negative Application Condition, express structures that cannot be present before or after applying a transformation rule.
	
\item[\bf Object Variable]
Bindable place holders for actual objects in the current model during pattern matching.

\item[\bf ObjectVariableExpression]
Refer to other object variables from preceding story nodes.

\item[\bf Parameter Expression]
Used to refer to the passed in method parameter.

\item[\bf (Graph) Pattern Matching]
Find occurrences of objects (from the typed graph) in a model.

\item[\bf Statement Nodes]
Cannot contain stop or start modes; Used to guarantee method invocation and execution.

\item[\bf Story Node]
Patterns that contain stop and start nodes (i.e., contain \emph{story pattern}s).

\item[\bf Story Pattern]
Implements a structure change in the model; Declarative transformation rules that the transformation must perform.

\item[\bf Unification]
An extension of the Object Oriented ``Everything is a object'' principle, where everything is classified as a \emph{model}, even the metamodel which defines
other models.

\end{description}
