\genHeader
\requiredTime{haven't decided yet}

Welcome to Part III, an introduction to unidirectional model transformations via programmed graph transformations using Story Driven Modeling (SDM).
SDMs focus on concrete implementations, so we plan to implement the methods signatures declared in the abstract styntax. It other words, this is where you'll
build your metamodel's dynamic semantics! Don't let the sheer size of this part frighten you off - we have included deep, thorough explanations with many
figures to ensure the concepts are crystal clear. It's really not that bad.

In Part II, we learned that we can implement methods in a straightforward manner with injections and Java code, so why bother with SDMs? 

Overall, SDMs are simply an alternate way of implementing methods. Rather than verbose Java code, you can model each task, then generate the implementation
code to incorporate the idea into existing code. With the visual syntax, the advantage is obvious. You'll be able to use familiar, easy-to-understamd UML
activity diagrams to establish your methods. Texually, SDMs extend the Objected Oriented Paradigm and separates all classes, references and links, and
activities into separate files, folders, and patterns.

% That was the advantage, but WHY do we use SDMs? (Motivation)

If you're just joining us, read the next section for a brief overview of our running example so far, and how to download some files that will help you get
started right away. If you're continuing from Part II, click the link below to continue with your constructed learning box metamodel.

\begin{center}\texttt{$\triangleright$ \hyperlink{explanation}{Continue from Part II\ldots}}\end{center}
